Smart Model Elimination for Efficient Automated Machine Learning

### 2024-06-21 paper/paper.tex
small change

\begin{table}
  \caption{Survey of Existing AutoML Frameworks}
  \label{automl-survey}
  \centering
  \begin{tabular}{lllllllll}
    \toprule
    Framework & EOU & M & FE & TM & HPT & Inter & Custom\\
    \midrule
    H2O AutoML & Easy & 6 & Basic & Yes & Auto & SHAP & High\\
    TPOT & Hard & 10 & Basic & No & Genetic & POJO & Moderate\\
    MLJAR & Easy & 12 & Advanced & Yes & Auto & Basic & High\\
    FLAML & Easy & 9 & Limited & Yes & Auto & SHAP & Low-Moderate\\
    LightAutoML & Easy & 11 & Advanced & Yes & Auto & Basic & Moderate\\
    \bottomrule
  \end{tabular}
  \captionsetup{font=footnotesize}
  \caption*{\textbf{Abbreviations}: EOU: Ease of Use, M: \# of models evaluated by framework, FE: Feature Engineering, TM: Time Management, HPT: Hyper-Parameter Tuning, Inter: Interface, Custom: Customization}
\end{table}
Table 1: Comparison of six AutoML frameworks based on commonmly evaluated criteria as well as more obscure features relevant to the medical diagnosis process

We systematically reviewed and compared six different AutoML frameworks, comparing every feature relevant to medical implementation. Of these six, we wanted to take a closer look at four: FLAML, H2O, MLJAR, and TPOT.

>>>>

\begin{table}
  \caption{Survey of Existing AutoML Frameworks}
  \label{automl-survey}
  \centering
  \begin{tabular}{lllllllll}
    \toprule
    Framework & EOU & M & FE & TM & HPT & Inter & Custom\\
    \midrule
    H2O AutoML & Easy & 6 & Basic & Yes & Auto & SHAP & High\\
    TPOT & Hard & 10 & Basic & No & Genetic & POJO & Moderate\\
    MLJAR & Easy & 12 & Advanced & Yes & Auto & Basic & High\\
    FLAML & Easy & 9 & Limited & Yes & Auto & SHAP & Low-Moderate\\
    LightAutoML & Easy & 11 & Advanced & Yes & Auto & Basic & Moderate\\
    \bottomrule
  \end{tabular}
  \captionsetup{font=footnotesize}
  \caption*{\textbf{Abbreviations}: EOU: Ease of Use, M: \# of models evaluated by framework, FE: Feature Engineering, TM: Time Management, HPT: Hyper-Parameter Tuning, Inter: Interface, Custom: Customization}
\end{table}
We systematically reviewed and compared six different AutoML frameworks, comparing every feature relevant to medical implementation. Of these six, we wanted to take a closer look at four: FLAML, H2O, MLJAR, and TPOT.
